\sys: Light-touch Data-Parallel Shell Processing

### 2020-10-08 paper/draft.tex
Corrections

@@

\heading{Highlights}
\sys accelerates ($1.92-61.1\times$) \todo{49/54} scripts, whereas for the rest 5 the parallel execution time is close to the sequential (0.89, 0.91, 0.94, 099, 1.01$\times$).
In this paragraph we summarize results for \ttt{--width=16}, but the rest of our evaluation section reports on varying \ttt{width}s.
For a subset of our benchmarks~\sx{ours}, we decouple the performance benefits stemming from \sys's DFG transformations alone from the ones stemming from its runtime primitives:
  the compiler's average speedup is \todo{$9.3\times$}, jumping to \todo{$13.2\times$} when runtime optimizations are used.
A different subset ($30$ benchmarks) see an average speedup of $6.02\times$~\sx{unix50}.
% , depending on the classed of commands involved
Two complex scripts with 15~\sx{macro1} and 34~\sx{macro2} commands in multiple languages see speedups of $2.44\times$ and $12.7\times$.
\sys outperforms \ttt{sort --parallel} by a significant margin, and offers small performance benefits over GNU \ttt{parallel}, which returns incorrect results in one configuration~\sx{micro}.
% Averages: [1.955223776839714, 3.478591807121036, 5.721328556478535, 8.604380509595906, 10.666921423438112, 13.246864076708423]
% No Eager Averages: [1.6327834370824543, 2.5481043878162444, 3.8623841529643173, 5.931851620007484, 7.466566647963421, 9.35752032439642]
% From the rest, only two see a slowdown, only because \sys's setup ($\sim1s$) is higher than their runtime ($\sim0.4s$).
% \sys's optimized primitives offer benefits even against manually parallelized scripts. % (such as GNU sort, and GNU parallel).
% \sys's compilation pass is negligible (avg. $<1s$). %  for non trivial program execution.
% In two large cases, tasks such as data download, extraction, and preprocessing---often implemented using shell scripts and outside the focus of specialized parallelization frameworks---take comparable time to the execution of the main computation, and can be significantly accelerated by \sys.
% In terms of manual effort,

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{\detokenize{./figs/tiling_throughput_scaleup.pdf}}
    \caption{
      \textbf{\sys's speedup for \ttt{width=} 2--64.}
      Different configurations per benchmark:
      (i) PaSh: the complete implementation with \ttiny{eager} and \ttiny{split} enabled,
      % (ii) Par+B.Split: \ttt{eager} and input-aware \ttt{split} enabled,
      (ii) PaSh w/o split: \ttiny{eager} enabled (no \ttiny{split}),
      (iii) \todo{Blocking Eager}, only blocking \ttiny{eager} enabled (no \ttiny{split}),
      (iv) \todo{No Eager}: both \ttiny{eager} and \ttiny{split} disabled.
  For some pairs of configurations, \sys produces identical parallel scripts and thus only one is shown.
%   Two types of pairs where x y z coincide
%   - \sys adds no split, whenever whenever the DFG width is constant for the entire pipeline. In these cases the blue line is identical to the red line, which not shown.
%    Conversely, whenever both blue and red lines are shown, split nodes are needed due to changes in the pipeline width and result in performance improvements.
% 
%   - without split, the script is sequential (spell, bigrams)
% Early on they have a pure or no parallelizable pure
% and thus introduce an aggregator resulting in width of 1 right after, and requires a split.
% Thus, any configuration that does not has \ttt{split} is practically sequential beyond that point---\ie No Eager, Blocking Eager, and \sys w/o Split see no speedup.
% 
% Blocking eager: data parallelism, but no task parallelism
% No eager: blocking FIFO does not allow pushing -> underutilize CPU
% 
% The reason why Blocking Eager is usually slower than No Eager is due to \ttt{agg}regators that read multiple input streams at the same time---such \ttt{sort -m}.
% 
% Sort-sort possibly shows the full spectrum:
%   (iii) \sys's \ttt{eager} offers benefits despite the lack of \ttt{split} because it fully parallelizes the first \ttt{sort} while maintaining task parallelism
%   (iv) \sys gets full benefits because \ttt{split}ting allows parallelizing the second \ttt{sort} too.

@@

      % (vi) Opt. Parallel, an optimized version of \ttt{bigrams}~\cf{ours}.
      % Only relevant configurations are shown---\eg \ttt{grep} and \ttt{sort} do not benefit from \ttt{split}; \ttt{spell} and \ttt{bi-grams} do not see benefits without \ttt{split}.
      % TODO: WHY?
    }
    \vspace{-15pt}
    \label{fig:microbenchmarks}
\end{figure*}

@@

We now evaluate \sys on an existing set of \unix pipelines found in the wild and \todo{written by non-experts}.
% \kk{OSDI reviewer asked how do you know if they are non-experts.}

\heading{Programs}
In a recent celebration of \unix's 50-year legacy, Bell Labs created 37 challenges~\cite{unix50} solvable by means of composing \unix pipelines.
The problems were designed to highlight \unix's modular philosophy~\cite{mcilroy1978unix}.
We found unofficial solutions to all-but-three problems on GitHub~\cite{unix50sol}, expressed as pipelines with 2--12 stages (avg.: 5.58).
They make extensive use of standard commands under a variety of flags, and appear to be written by non-experts (contrary to \S\ref{ours}, they often use sub-optimal or non-\unix-y constructs).
% ---stressing a patterns that we, \sys's authors, did not
% necessarily anticipate \kk{I would change that to ``stressing a
%   variety of patterns'' since it doesn't really matter if we
%   anticipated them (especially since we can address any issues and
%   then re-run them).} . 
\sys executes each pipeline as-is, without any modification.
  % if an obvious fix improves performance, we report the speedup of both versions. %  original and modified. %  pipeline.

@@

\heading{Results}
\sys's parallelism is set to $16\times$, as many of these pipelines are relatively long (\S\ref{eval}, Parallelism).
Their input was generated by \todo{multiplying their original input several times, enough to reach 10GB.}
% \kk{eurosys: One OSDI reviewer didn't like how this is phrased. Can we change that?}
Fig.~\ref{fig:unix50-individual} shows the speedup (left) over the sequential runtime (right) for all \todo{30} pipelines. We use the pipeline index to refer to them in both plots and discussion.
%% (\nv{Pipelines are referred by number, in both the plot and the discussion below.})
Average speedup is \todo{$6.02\times$}, median is $6.48\times$, and weighted average (with the absolute times as weights) is $5.75\times$.
 % the \todo{geometric mean is $1.08\times$},
We do not include three pipelines that take less than 0.1 seconds to execute because they only output the first line of their input using \ttt{head}.

@@

\heading{Discussion}
Most pipelines see significant acceleration, except 25-30
  % \todo{13, 24, 25, 26, 29, 30} 
  that see no speedup. 
  % and \todo{2, 19, 31} that see a slowdown.
These pipelines contain commands which \sys cannot parallelize without risking breakage---\eg \ttt{awk} and \ttt{sed} \ttt{-d}. % and \ttt{tr} \ttt{-d}.
Note however, that some of the pipelines contain more general commands that cannot be parallelized since they were not written with that goal in mind; a common example is the use of \ttt{awk} for reordering or removing columns of the input.
%% Some of them use general interpreters when they could be using a specialized equivalent tailored to the task at hand, the typical example being \ttt{awk} vs \ttt{cut}.
In particular, replacing an \ttt{awk} that was just used to sort on the second field \ttt{awk "{print \$2, \$0}" | sort -nr} with a single \ttt{sort -nr -k 2} in the 
  % \todo{13th} 
  26th pipeline allows \sys to achieve 8.1$\times$ speedup (in contrast to the original 1.01$\times$).
%% , attempting only such obvious (to us, experts) replacements, \sys extracts further parallelism---\eg 13 sees a 8.1$\times$ speedup.
% ---a common pattern we witnessed~\sx{macro1}.

@@

For the rest, \sys's speedup is capped due to a combination of reasons:
  (i) they contain pure commands that are parallelizable but don't scale linearly, such as \ttt{sort} 
  5, 6, 7, 8, 9, 19, 20, 21, 23, 24,
  % 24, 9, 7, 6, 8, 23, 20, 19, 21, 5
  % \todo{(0, 1, 3, 15, 16, 18, 20, 27, 28, 33)},
  (ii) some are deep pipelines that already exploit task-based parallelism 
  4, 10, 11, 13, 15, 17, 19, 21, 22,
  % 17, 4, 13, 15, 10, 22, 11, 19, 21,
  % \todo{(7, 8, 9, 10, 11, 12, 14, 27, 28,)} 
  and
  (iii) they are not CPU-intensive, resulting in pronounced IO and constant costs 
  3, 4, 11, 12, 14, 16, 17, 18, 22.
  % 14, 3, 16, 17, 4, 22, 11, 12, 18
  % \todo{(4, 5, 6, 7, 8, 12, 14, 22, 23)}.

@@

\heading{Program}
This program is inspired by Hadoop's Definitive Guide~\cite[Chapter 2]{hadoop:15}, where it exemplifies a realistic analytics pipeline comprising three sub-tasks:
  fetch data from NOAA (shell), convert them to a Hadoop-friendly format (shell), and calculate the maximum temperature (Hadoop).
Only the last one is the real focus of the book, % demonstrating the benefits of using distributed framework such as Hadoop.
  whereas we consider the entire pipeline. % ---from fetching data to outputting the maximum temperature.
% The version used in the evaluation is slightly different than the one presented in Fig.~\ref{fig:example} (14 stages and totalling 240 characters), simplified only for clarity of exposition, in that it expresses the \ttt{for} loop as a first stage followed by \ttt{xargs}.

\heading{Results}
The complete pipeline executes in 44m2s for five years (82GB) of data.
\sys with \todo{10$\times$ parallelism} leads to \todo{2.44$\times$} speedup, with different phases seeing different benefits:
  \todo{1.99$\times$} (vs. 33m58s) for all the pre-processing and 
  \todo{10.79$\times$} speedup (vs. 10m4s) for computing the max.
\todo{The reason why speedup is higher than parallelism} is explained at the beginning of \S\ref{eval} (Parallelism).\footnote{
  \nv{Can we avoid this by not showing the $2\times$? Why show $2\times$?} % <--- Eurosys
  \kk{This will probably not be the case if we run for x16}
}

@@

\heading{Take-aways}
\sys can be applied to programs of notable size and input to offer significant acceleration.
A broader take-away is that \sys is also able to extract parallelism from fragments that are not purely compute-intensive regions, \ie the usual focus of conventional parallelization systems.

@@

\heading{Results}
% To simplify execution (and avoid Wikipedia), we have saved a recent Wikipedia version on a server within the network and to redirect all \ttt{curl} requests there.
%% As the \todo{first} component contains a cycle (URLs $\rightarrow$ HTML $\rightarrow$ URLs), \sys's conservative transformations do not attempt to parallelize it.
The original script takes 191min to execute on 1\% of Wikipedia (1.3GB).
With 16$\times$\todo{-parallelism}, \sys brings it down to 15min ($12.7\times$), with the majority of the speedup coming from the HTML-to-text conversion. % which uses \ttt{pandoc}, a utility written in Haskell.

@@

\heading{Take-aways}
\sys operates on programs with annotated commands outside the POSIX/GNU subsets and leads to notable speedups even when the original program features significant task-based parallelism.

@@

This section attempts to characterize \sys's limits by comparing it with similar alternatives.
As there are no prior systems directly comparable to \sys, we draw comparisons with a series of specialized ones that excel within smaller fragments of \sys's proposed domain.

\pichskip{15pt}% Horizontal gap between picture and text
\parpic[r][t]{%
  \begin{minipage}{40mm}
    \includegraphics[width=\linewidth]{\detokenize{./figs/sort_baseline_comparison_scaleup.pdf}}%
    %% \captionof{figure}{This is a tiger.}
  \end{minipage}
}
\heading{Parallel Sort}
%% \kk{Explain what is the purpose of the
%%   microbenchmark. We want to establish that \sys scalability is as
%%   good as it could be.}
We first compare a single GNU \ttt{sort} parallelized by \sys ($S_{PaSh}$) versus the same \ttt{sort} with the 
%% \begin{wrapfigure}[10]{r}{0.25\textwidth}
%%   \centering
%%   %% \begin{center}
%%     \includegraphics[width=0.25\textwidth]{\detokenize{./figs/sort_baseline_comparison_scaleup.pdf}}
%%   %% \end{center}
%% %   \vspace{-15pt}
%% % \caption{ \textbf{Comparison with \ttt{sort -{}-parallel}.} }
%% \end{wrapfigure}
\ttt{--parallel} flag set ($S_{GNU}$). % , shown on the side.
% The results are shown on the side-figure below.
While \ttt{--parallel} is not a general solution, the comparison serves to establish a baseline for \sys.
$S_{GNU}$'s parallelism is configured to $2\times$ that of \todo{$S_{PaSh}$'s} \ttt{--width} (\ie the rightmost plot point for $S_{GNU}$ is for \ttt{--parallelism=128}), 
to account for \sys's additional runtime processes.
% and as such we note that the measurements are harsh for \sys.

A few points are worth noting.
$S_{PaSh}$ without \ttt{eager} performs comparably to $S_{GNU}$, and with \ttt{eager} it outperforms $S_{GNU}$ ($\sim2\times$);
  this is because \ttt{eager} adds intermediate buffers %(on disk)
  that ensure CPU utilization is high.
%% On the other hand, \ttt{sort --parallel} sorts the input trying to
%% minimize additional memory (so doesn't allocate intermediate
%% buffers).
%% %% \kk{If we want, we can add here numbers where we allow sort --parallel
%% %%   to use additional ram for intermediate buffers (using the -S flag).}
%% Of course, it would be possible to manually create a longer pipeline
%% and use intermediate buffers to speed this up, but this defeats the
%% purpose of having a simple solution.
$S_{GNU}$ indicates that \ttt{sort}'s scalability is inherently limited (\ie due to \ttt{sort} and not \sys);
  this is why all scripts that contain \ttt{sort} (\eg \S\ref{ours}--\ref{macro2}) do not go above $8\times$.
Finally, the comparison also shows \sys's benefits to command developers:
  a low-effort parallelizability annotation achieves better scalability than a custom flag (and underlying parallel implementation) manually added by developers.

@@

\heading{GNU Parallel}
We compare \sys to \ttt{parallel} (v.20160422), a GNU utility for running other commands in parallel~\cite{Tange2011a}, on a small bio-informatics script.
% Using its \ttt{--jobs} flag, we  redirect input from a file to 
% 554 / 330 
Sequential execution takes 554.8s \vs \sys's 128.5s (4.3$\times$).
We note that this pipeline is harsh for \sys, in that most of the overhead comes from a single command---masking \sys's improvements in other parts of the pipeline.

@@

There are a few possible ways one might attempt to use GNU \ttt{parallel} on this program.
They could use it on the bottleneck stage, assuming they are can deduce that, bringing execution down to 304.4s ($1.8\times$ speedup).
Alternatively, they could (incorrectly) sprinkle \ttt{parallel} across the entire program---a strategy simplified by \ttt{parallel}'s \ttt{stdin} redirection feature.
This would lead to 3.2$\times$ performance improvements but severely incorrect results with respect to the sequential execution---with 92\% of the output showing a difference between sequential and parallel execution.
\sys's conservative program transformations are not applied in program fragments with unclear parallelizability properties.
	% or commands whose inputs depend on earlier outputs.
% GNU \ttt{parallel} is oblivious to command semantics, risking breaking program semantics as in this case.

>>>>

% TODO: keep only points necessary for the punchline 
% In the vast majority of scripts (49/54), \sys achieves significant speedups \todo{(average for width=16)}, and for the rest 5 slowdown is insignificant (worst case 0.89x).
% For the temperature analysis script (which is taken from a Hadoop case study), \sys not only 
% contains pre-processing that takes X time and Y main processing (Hadoop focus).
% \sys accelerates the entire pipeline by , including the fragment that is outside the focus of conventional parallelization systems.
% accelerates the CPU-intensive part that is parallelized by Hadoop, but also for the preprocessing part which takes even more time than what the other part takes.
% XX--YY speedups in the vast majority of scripts, ones taken from the wild 
% 1. Sentence about transformations vs runtime primitives
% 2. Unix 50? 
% 3. point about Hadoop expressing a fraction of the pipeline and speedup
% \sys achieves higher speedup than \ttt{sort --parallel} that involved hand-tuned parallel implementation by command developers.
% correctness of GNU parallel
% PaSh can be applied to programs of notable
% size and input to offer significant acceleration. A broader
% take-away is that PaSh is also able to extract parallelism from
% fragments that are not purely compute-intensive regions, i.e.,
% the usual focus of conventional parallelization systems.

@@

\heading{Highlights}
\sys accelerates ($1.92-61.1\times$) \todo{49/54} scripts, whereas for the rest 5 the parallel execution time is close to the sequential (0.89, 0.91, 0.94, 099, 1.01$\times$).
In this paragraph we summarize results for \ttt{--width=16}, but the rest of our evaluation section reports on varying \ttt{width}s.
For a subset of our benchmarks~\sx{ours}, we decouple the performance benefits stemming from \sys's DFG transformations alone from the ones stemming from its runtime primitives:
  the compiler's average speedup is \todo{$9.3\times$}, jumping to \todo{$13.2\times$} when runtime optimizations are used.
A different subset ($30$ benchmarks) see an average speedup of $6.02\times$~\sx{unix50}.
% , depending on the classed of commands involved
Two complex scripts with 15~\sx{macro1} and 34~\sx{macro2} commands in multiple languages see speedups of $2.44\times$ and $12.7\times$.
\sys outperforms \ttt{sort --parallel} \todo{by a significant margin}\footnote{
\nv{Nikos add point about experts}
}, and performs better than GNU \ttt{parallel}, which returns incorrect results if used without care~\sx{micro}.
% Averages: [1.955223776839714, 3.478591807121036, 5.721328556478535, 8.604380509595906, 10.666921423438112, 13.246864076708423]
% No Eager Averages: [1.6327834370824543, 2.5481043878162444, 3.8623841529643173, 5.931851620007484, 7.466566647963421, 9.35752032439642]
% From the rest, only two see a slowdown, only because \sys's setup ($\sim1s$) is higher than their runtime ($\sim0.4s$).
% \sys's optimized primitives offer benefits even against manually parallelized scripts. % (such as GNU sort, and GNU parallel).
% \sys's compilation pass is negligible (avg. $<1s$). %  for non trivial program execution.
% In two large cases, tasks such as data download, extraction, and preprocessing---often implemented using shell scripts and outside the focus of specialized parallelization frameworks---take comparable time to the execution of the main computation, and can be significantly accelerated by \sys.
% In terms of manual effort,

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{\detokenize{./figs/tiling_throughput_scaleup.pdf}}
    \caption{
      \textbf{\sys's speedup for \ttt{width=} 2--64.}
      Different configurations per benchmark:
      (i) PaSh: the complete implementation with \ttiny{eager} and \ttiny{split} enabled,
      % (ii) Par+B.Split: \ttt{eager} and input-aware \ttt{split} enabled,
      (ii) PaSh w/o split: \ttiny{eager} enabled (no \ttiny{split}),
      (iii) \todo{Blocking Eager}, only blocking \ttiny{eager} enabled (no \ttiny{split}),
      (iv) \todo{No Eager}: both \ttiny{eager} and \ttiny{split} disabled.
  For some pairs of configurations, \sys produces identical parallel scripts and thus only one is shown.
}
%   Two types of pairs where x y z coincide
%   - \sys adds no split, whenever whenever the DFG width is constant for the entire pipeline. In these cases the blue line is identical to the red line, which not shown.
%    Conversely, whenever both blue and red lines are shown, split nodes are needed due to changes in the pipeline width and result in performance improvements.
% 
%   - without split, the script is sequential (spell, bigrams)
% Early on they have a pure or no parallelizable pure
% and thus introduce an aggregator resulting in width of 1 right after, and requires a split.
% Thus, any configuration that does not has \ttt{split} is practically sequential beyond that point---\ie No Eager, Blocking Eager, and \sys w/o Split see no speedup.
% 
% Blocking eager: data parallelism, but no task parallelism
% No eager: blocking FIFO does not allow pushing -> underutilize CPU
% 
% The reason why Blocking Eager is usually slower than No Eager is due to \ttt{agg}regators that read multiple input streams at the same time---such \ttt{sort -m}.
% 
% Sort-sort possibly shows the full spectrum:
%   (iii) \sys's \ttt{eager} offers benefits despite the lack of \ttt{split} because it fully parallelizes the first \ttt{sort} while maintaining task parallelism
%   (iv) \sys gets full benefits because \ttt{split}ting allows parallelizing the second \ttt{sort} too.

@@

      % (vi) Opt. Parallel, an optimized version of \ttt{bigrams}~\cf{ours}.
      % Only relevant configurations are shown---\eg \ttt{grep} and \ttt{sort} do not benefit from \ttt{split}; \ttt{spell} and \ttt{bi-grams} do not see benefits without \ttt{split}.
      % TODO: WHY?
    \vspace{-15pt}
    \label{fig:microbenchmarks}
\end{figure*}

@@

We now evaluate \sys on an existing set of \unix pipelines found in the wild.

\heading{Programs}
In a recent celebration of \unix's 50-year legacy, Bell Labs created 37 challenges~\cite{unix50} solvable by \unix pipelines.
The problems were designed to highlight \unix's modular philosophy~\cite{mcilroy1978unix}.
We found unofficial solutions to all-but-three problems on GitHub~\cite{unix50sol}, expressed as pipelines with 2--12 stages (avg.: 5.58).
They make extensive use of standard commands under a variety of flags, and appear to be written by non-experts (contrary to \S\ref{ours}, they often use sub-optimal or non-\unix-y constructs).
% ---stressing a patterns that we, \sys's authors, did not
% necessarily anticipate \kk{I would change that to ``stressing a
%   variety of patterns'' since it doesn't really matter if we
%   anticipated them (especially since we can address any issues and
%   then re-run them).} . 
\sys executes each pipeline as-is, without any modification.
  % if an obvious fix improves performance, we report the speedup of both versions. %  original and modified. %  pipeline.

@@

\heading{Results}
\sys's \ttt{width} is set to 16 and pipelines are given 10GB inputs.
Fig.~\ref{fig:unix50-individual} shows the speedup (left) over the sequential runtime (right) for 31 pipelines.
We do not include three pipelines that take less than 0.1 seconds to execute because they only output the first line of their input using \ttt{head}.
We use the pipeline index to refer to them in both plots and discussion.
Average speedup is \todo{$6.02\times$}, median is $6.48\times$, and weighted average (with the absolute times as weights) is $5.75\times$.
 % the \todo{geometric mean is $1.08\times$},

@@

\heading{Discussion}
Most pipelines see significant acceleration, except 25-30
  % \todo{13, 24, 25, 26, 29, 30} 
  that see no speedup. 
  % and \todo{2, 19, 31} that see a slowdown.
These pipelines often contain general commands that \sys cannot parallelize without risking breakage---\eg \ttt{awk} and \ttt{sed} \ttt{-d}. % and \ttt{tr} \ttt{-d}.
% Note however, that some of the pipelines contain more general commands that cannot be parallelized since they were not written with that goal in mind;
%   a common example is the use of \ttt{awk} for reordering or removing columns of the input.
%% Some of them use general interpreters when they could be using a specialized equivalent tailored to the task at hand, the typical example being \ttt{awk} vs \ttt{cut}.
A \unix expert would notice that some of these uses could be replaced with \unix-specific commands---\eg replacing \ttt{awk "{print \$2, \$0}" | sort -nr} just used to sort on the second field with a single \ttt{sort -nr -k 2} in the 26th pipeline.
  % \todo{13th} 
The limited expressiveness of these commands can be exploited by \sys---in this specific case, achieving 8.1$\times$ speedup (\vs the original 1.01$\times$).
%% , attempting only such obvious (to us, experts) replacements, \sys extracts further parallelism---\eg 13 sees a 8.1$\times$ speedup.
% ---a common pattern we witnessed~\sx{macro1}.

@@

For the rest, \sys's speedup is capped due to a combination of reasons:
  (i) they contain pure commands that are parallelizable but don't scale linearly, such as \ttt{sort} 
  (\# 5, 6, 7, 8, 9, 19, 20, 21, 23, 24), 
  % 24, 9, 7, 6, 8, 23, 20, 19, 21, 5
  % \todo{(0, 1, 3, 15, 16, 18, 20, 27, 28, 33)},
  (ii) they are deep pipelines that already exploit task-based parallelism
  (\# 4, 10, 11, 13, 15, 17, 19, 21, 22),
  % 17, 4, 13, 15, 10, 22, 11, 19, 21,
  % \todo{(7, 8, 9, 10, 11, 12, 14, 27, 28,)} 
or 
  (iii) they are not CPU-intensive, resulting in pronounced IO and constant costs 
  (\# 3, 4, 11, 12, 14, 16, 17, 18, 22).
  % 14, 3, 16, 17, 4, 22, 11, 12, 18
  % \todo{(4, 5, 6, 7, 8, 12, 14, 22, 23)}.

@@

\heading{Program}
This program is inspired by Hadoop's Definitive Guide~\cite[Chapter 2]{hadoop:15}, where it exemplifies a realistic analytics pipeline comprising three sub-tasks:
  fetch data from NOAA (shell), convert them to a Hadoop-friendly format (shell), and calculate the maximum temperature (Hadoop).
While the book focuses only on the last one, \sys parallelizes the entire pipeline.
% Only the last one is the real focus of the book, % demonstrating the benefits of using distributed framework such as Hadoop.
%   whereas we consider the entire pipeline. % ---from fetching data to outputting the maximum temperature.
% The version used in the evaluation is slightly different than the one presented in Fig.~\ref{fig:example} (14 stages and totalling 240 characters), simplified only for clarity of exposition, in that it expresses the \ttt{for} loop as a first stage followed by \ttt{xargs}.

\heading{Results}
The complete pipeline executes in 44m2s for five years (82GB) of data.
\sys with \ttt{width=}16 leads to \todo{2.44$\times$} speedup, with different phases seeing different benefits:
  \todo{1.99$\times$} (vs. 33m58s) for all the pre-processing and 
  \todo{10.79$\times$} speedup (vs. 10m4s) for computing the max.

@@

\heading{Take-aways}
\sys can be applied to programs of notable size \todo{and complexity} to offer significant acceleration.
A broader take-away is that \sys is also able to extract parallelism from fragments that are not purely compute-intensive regions, \ie the usual focus of conventional parallelization systems.

@@

\heading{Results}
% To simplify execution (and avoid Wikipedia), we have saved a recent Wikipedia version on a server within the network and to redirect all \ttt{curl} requests there.
%% As the \todo{first} component contains a cycle (URLs $\rightarrow$ HTML $\rightarrow$ URLs), \sys's conservative transformations do not attempt to parallelize it.
The original script takes 191min to execute on 1\% of Wikipedia (1.3GB).
With \ttt{width=}16, \sys brings it down to 15min ($12.7\times$), with the majority of the speedup coming from the HTML-to-text conversion. % which uses \ttt{pandoc}, a utility written in Haskell.

@@

\heading{Take-aways}
\sys operates on programs with (annotated) commands outside the POSIX/GNU subsets and leads to notable speedups, even when the original program features significant task-based parallelism.

@@

% This section attempts to compare \sys with best-of-breed alternatives for particular taks.
As there are no prior systems directly comparable to \sys, this section draws comparisons with two specialized cases that excel within smaller fragments of \sys's proposed domain.

\pichskip{15pt}% Horizontal gap between picture and text
\parpic[r][t]{%
  \begin{minipage}{40mm}
    \includegraphics[width=\linewidth]{\detokenize{./figs/sort_baseline_comparison_scaleup.pdf}}%
    %% \captionof{figure}{This is a tiger.}
  \end{minipage}
}
\heading{Parallel Sort}
%% \kk{Explain what is the purpose of the
%%   microbenchmark. We want to establish that \sys scalability is as
%%   good as it could be.}
We first compare a single GNU \ttt{sort} parallelized by \sys ($S_{PaSh}$) \vs the same \ttt{sort} with the 
%% \begin{wrapfigure}[10]{r}{0.25\textwidth}
%%   \centering
%%   %% \begin{center}
%%     \includegraphics[width=0.25\textwidth]{\detokenize{./figs/sort_baseline_comparison_scaleup.pdf}}
%%   %% \end{center}
%% %   \vspace{-15pt}
%% % \caption{ \textbf{Comparison with \ttt{sort -{}-parallel}.} }
%% \end{wrapfigure}
\ttt{--parallel} flag set ($S_{GNU}$). % , shown on the side.
% The results are shown on the side-figure below.
While \ttt{--parallel} is not a general solution, the comparison serves to establish a baseline for \sys.
$S_{GNU}$'s parallelism is configured to $2\times$ that of \todo{$S_{PaSh}$'s} \ttt{--width} (\ie the rightmost plot point for $S_{GNU}$ is for \ttt{--parallelism=128}), 
to account for \sys's additional runtime processes.
% and as such we note that the measurements are harsh for \sys.

A few points are worth noting.
$S_{PaSh}$ without \ttt{eager} performs comparably to $S_{GNU}$, and with \ttt{eager} it outperforms $S_{GNU}$ ($\sim2\times$);
  this is because \ttt{eager} adds intermediate buffers %(on disk)
  that ensure CPU utilization is high.
%% On the other hand, \ttt{sort --parallel} sorts the input trying to
%% minimize additional memory (so doesn't allocate intermediate
%% buffers).
%% %% \kk{If we want, we can add here numbers where we allow sort --parallel
%% %%   to use additional ram for intermediate buffers (using the -S flag).}
%% Of course, it would be possible to manually create a longer pipeline
%% and use intermediate buffers to speed this up, but this defeats the
%% purpose of having a simple solution.
$S_{GNU}$ indicates that \ttt{sort}'s scalability is inherently limited (\ie due to \ttt{sort} and not \sys);
  this is why all scripts that contain \ttt{sort} (\eg \S\ref{ours}--\ref{macro2}) are capped at $8\times$ speedup.
Finally, the comparison also shows \sys's benefits to command developers:
  a low-effort parallelizability annotation achieves better scalability than a custom flag (and underlying parallel implementation) manually added by developers.

@@

\heading{GNU Parallel}
We compare \sys to \ttt{parallel} (v.20160422), a GNU utility for running other commands in parallel~\cite{Tange2011a}, on a small bio-informatics script.
% Using its \ttt{--jobs} flag, we  redirect input from a file to 
% 554 / 330 
Sequential execution takes 554.8s \vs \sys's 128.5s (4.3$\times$), with most of the overhead coming from \todo{a single command}.

@@

There are a few possible ways users might attempt to use GNU \ttt{parallel} on this program.
They could use it on the bottleneck stage, assuming they can deduce it, bringing execution down to 304.4s ($1.8\times$ speedup).
Alternatively, they could (incorrectly) sprinkle \ttt{parallel} across the entire program.
% ---a strategy simplified by \ttt{parallel}'s \ttt{stdin} redirection feature.
This would lead to 3.2$\times$ performance improvements but incorrect results with respect to the sequential execution---with 92\% of the output showing a difference between sequential and parallel execution.
\sys's conservative program transformations are not applied in program fragments with unclear parallelizability properties.
	% or commands whose inputs depend on earlier outputs.
% GNU \ttt{parallel} is oblivious to command semantics, risking breaking program semantics as in this case.
